---
title: "Simulation Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simulation Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(TWASKnockoff)
```

We generate individual-level gene expression levels and phenotypes based on 503 non-overlapping Europeans from 1000 Genomes (1KG) phase 3 (https://www.cog-genomics.org/plink/2.0/resources). We simulate a risk region including 950 cis-SNPs and 5 candidate genes. Each gene contains 100 cis-SNPs, including 2 eQTLs explaining 20% variation of gene expression levels. Only the first gene is causal to the trait of interest, explaining 50% of total heritability, which is set to 0.2. The remaining heritability is explained by 5 non-mediated causal SNPs.

We calculate the summary statistics (z-scores) for each cis-SNP in the risk region based on simulated phenotype and in-sample genotype data. For this example, we used the in-sample genotype to replace the reference panel.

```{r}
str(data)
```

We run TWASKnockoff with the following code:

```{r}
set.seed(100)

# number of genes
k = length(data$ye)
# indices of cis-variants for each candidate gene in the risk region
snpidx = data$snpidx 
# gene expression levels for each gene in the eQTL study
ye = data$ye 
# cis-genotype matrices for each gene in the eQTL study
Xe = data$Xe 
# summary statistics for cis-SNPs in the risk region
summarystat = data$summary_stats 
# cis-genotype matrix from reference panel for the risk region
Xp = data$Xp 
# predicted gene expression levels based on the eQTL model in the reference panel
yep_true <- data$yep_true 


correlation = 'improved'
ts = 'marginal'

result = TwasKnockoff(snpidx = snpidx, ye = ye, Xe = Xe, 
             summarystat = summarystat, Xp = Xp, 
             removemethod = 'lasso', 
             correlation = correlation, nrep = 10, ts = ts, yep_true = yep_true)

print(result$GK.filter$kappa[1:k])
print(result$GK.filter$tau[1:k])
print(result$GK.filter$q[1:k])
```

The 
